Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-04-25 paper.tex
Start to add more to experiments section and update training algo.

@@

%%%%%%%%% TITLE
\title{Multi-task Mutual Learning for Vehicle Re-Identification}

@@

In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn an feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation. In order to perform this task, we utilise training data containing a number of different labels: identity class labels, vehicle orientation class labels, and landmark position labels for a number of specific keypoints. We assume two sets of training examples $\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively. Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets. However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ and $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$

@@

As we have two training sets, each of which contain different groundtruth labels.

\begin{algorithm}[t]
  \caption{The model training algorithm}
  \label{A:model_training}
  \begin{algorithmic}
    \REQUIRE{Training sets $\mathcal{I}_1$ $\mathcal{I}_2$, labels $\mathcal{Y}_1$\
      $\mathcal{O}$ $\mathcal{L}$ $\mathcal{Y}_2$, model $\mathcal{M}$}
    \STATE{$\bullet$ Initialise network branches with pre-trained ImageNet weights}
    \STATE{$\bullet$ Initialise output layers of $\mathcal{M}$ randomly}

@@

      \FOR{each training set $\mathcal{I} \in (\mathcal{I}_1,\mathcal{I}_2)$}
        \STATE{$\bullet$ Feed-forward through model to obtain all branch identity classification \
        predictions on images in $\mathcal{I}$}

        \IF{$\mathcal{I}$ has associated $\mathcal{O}$ and $\mathcal{L}$}
          \STATE{$\bullet$ Feed-forward to obtain orientation classification and landmark regression \
        predictions}
        \ENDIF

        \STATE{$\bullet$ Fuse features and perform consensus identity classification predictions}
        \STATE{$\bullet$ Calculate hard and soft losses for each branch and backpropagate to update weights}
        \STATE{$\bullet$ Calculate hard and soft losses for the consensus branch and backpropagate}

      \ENDFOR
    \ENDFOR

@@

Details:
- Learning rate of ...
- Batch size 16?
- Number of epochs.

\subsection{Vehicle Benchmark Datasets}

\begin{table}
  \begin{tabular}{l || c | c || c | c }
    \hline
    \multirow{2}{*}{Method} & \multicolumn{2}{c ||}{VeRi776} & \multicolumn{2}{c}{VeRi776+VehicleID} \\
    \cline{2-5}
    & mAP & Rank-1 & mAP & Rank-1 \\
    \hline
    DPFL \cite{kanaci2018vehicle} & \\
    \hline
    MTML-S & \\
    MTML-O & \\
    MTML-G & \\
    \hline
    MTML-SG & \\
    MTML-OG & \\
    MTML-OSG & \\
    \hline

  \end{tabular}
  \caption{}
  \label{T:benchmark_results}
\end{table}

@@

\begin{table}
  \begin{tabular}{l || c | c}

>>>>

\def\x{{\mathsf x}}

@@

%%%%%%%%% TITLE
\title{Multi-Task Mutual Learning for Vehicle Re-Identification}

@@

In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn an feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation. In order to perform this task, we utilise training data containing a number of different labels: identity class labels, vehicle orientation class labels, and landmark position labels for a number of specific keypoints. We assume two sets of training examples $\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively. Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets. However, in addition, $\mathcal{I}_1$ also contains orientation labels, $\mathcal{O_1}=\{o_i\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations).
%and landmark position labels $\mathcal{L_1}=\{\mathbf{l_i}\}_{i=1}^N$ $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$

@@

In order to train our model, we combine both training sets, $\mathcal{I}_1$ and $\mathcal{I}_2$, and employ batches that contain both images with and without orientation labelling.

\begin{algorithm}[t]
  \caption{The model training algorithm}
  \label{A:model_training}
  \begin{algorithmic}
    \REQUIRE{Training sets $\mathcal{I}_1$ $\mathcal{I}_2$, labels $\mathcal{Y}_1$ $\mathcal{Y}_2$\
      $\mathcal{O}_1$, model $\mathcal{M}$}
    \STATE{$\bullet$ Initialise network branches with pre-trained ImageNet weights}
    \STATE{$\bullet$ Initialise output layers of $\mathcal{M}$ randomly}

@@

        \STATE{$\bullet$ Feed-forward through model to obtain all branch identity classification \
          predictions on images in $\mathcal{I}_1$ and $\mathcal{I}_2$}
        \STATE{$\bullet$ Feed-forward to obtain orientation classification predictions on $\mathcal{I}_1$}
        \STATE{$\bullet$ Fuse features and perform consensus identity classification predictions on both training sets}
        \STATE{$\bullet$ Calculate hard and soft losses identity losses for each branch and backpropagate to update weights}
        \STATE{$\bullet$ Calculate orientation losses using labels for $\mathcal{I}_1$ and backpropagate to update weights on the orientation branch}
        \STATE{$\bullet$ Calculate hard and soft identity losses for the consensus branch and backpropagate}
     \ENDFOR

@@

Details:
- Learning rate of 0.0001
- Batch size 8
- Number of epochs.
- Adam optimiser with exponential decay rates set as follows: $\beta_1=0.9$ and $\beta_2=0.999$.
- The two scales used: standard $224\x224$ and small (for multiscale) $160\x160$.

We measure the performance of our vehicle re-identification methods according to the standard Cumulative Matching Characteristic (CMC) and mean Average Precision (mAP). The CMC is computed on each individual rank $k$ as the cumulative percentage of correct matches appearing
at ranks $\leq k$. The mAP is calculated as the mean over all query images of the Average Precision, which itself is calculated as the precision cut-off at each correct recalled image position averaged over all possible correct gallery images \cite{}.

\subsection{Vehicle Re-identification Datasets}

\paragraph{VeRi776}

\paragraph{VehicleID}

\paragraph{BoxCars21k}

\paragraph{CompCars}

\begin{table}
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    DPFL \cite{kanaci2018vehicle} & \\
    \hline
    MTML-S & \\
    MTML-O & \\
    MTML-G & \\
    \hline
    MTML-SG & \\
    MTML-OG & \\
    MTML-OSG & \\
    \hline
    MTML-OSG+ReRank & \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi776 only}
  \label{T:benchmark_results_veri}
\end{table}

\begin{table*}
  \centering
  \begin{tabular}{l || c | c || c | c || c | c }
    \hline
    \multirow{2}{*}{Method} & \multicolumn{2}{c}{Small} & \multicolumn{2}{c}{Medium} &\multicolumn{2}{c}{Large} \\
    \cline{2-7}
    & mAP & Rank-1 & mAP & Rank-1 & mAP & Rank-1 \\
    \hline
    DPFL \cite{kanaci2018vehicle} & \\
    \hline
    MTML-S & \\
    MTML-O & \\
    MTML-G & \\
    \hline
    MTML-SG & \\
    MTML-OG & \\
    MTML-OSG & \\
    \hline
    MTML-OSG+ReRank & \\
    \hline
  \end{tabular}
  \caption{Trained on VeRi776+VehicleID, tested on VehicleID}
  \label{T:benchmark_results_vehicleid}
\end{table*}

@@

\begin{table}
  \centering
  \begin{tabular}{l || c | c}
